Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-01 paper/manuscript.tex
Add some details to supp fig 1

\begin{suppfigure}
\centerline{\includegraphics[width=\textwidth]{figs/S01_G78D-T212I/G78D-T212I.pdf}}
\caption{\label{suppfig:Perth2009_mut}
{\bf Characterization of the G78D-T212I Perth/2009 HA variant.} 
(A) 
The G78D-T212I Perth/2009 HA variant grows to higher titers than do viruses carrying the wildtype Perth/2009 HA.
Each virus was generated in duplicate by reverse genetics and passaged once at MOI = 0.01 in MDCK-SIAT1-TMPRSS2 cells.
The rescue and passage viral supernatants were titered, with the points marking each duplicate and the bar marking the mean.
(B)
The D78 variant remained at a low frequency in natural human H3N2 sequences over the past $~\sim$10 years.
The A212 variant rose to fixation in $~\sim$2011, replacing the T212 variant.
}
\end{suppfigure}

>>>>

\begin{suppfigure}
\centerline{\includegraphics[width=\textwidth]{figs/S01_G78D-T212I/G78D-T212I.pdf}}
\caption{\label{suppfig:Perth2009_mut}
{\bf Characterization of the G78D-T212I Perth/2009 HA variant.} 
(A) 
The G78D-T212I Perth/2009 HA variant grows to higher titers than do viruses carrying the wildtype Perth/2009 HA.
Each virus was generated in duplicate by reverse genetics and passaged once at MOI = 0.01 in MDCK-SIAT1-TMPRSS2 cells.
The rescue and passage viral supernatants were collected at 72 hours post-transfection and 44 hours post-infection, respectively, and titered in MDCK-SIAT1-TMPRSS2 cells. 
The points mark each duplicate and the bar marks the mean.
(B)
The D78 variant remained at a low frequency in natural human H3N2 sequences over the past $~\sim$10 years.
The A212 variant rose to fixation in $~\sim$2011, replacing the T212 variant.
}
\end{suppfigure}
